---
title: "Leaflet"
author: "Paul Bruynel"
date: "12 July 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## My first map with Leaflet
```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>%
  addTiles()
my_map
```

## Add markers
You can add markers to your map one at a time using the
`addMarkers()` function by specifying the longitude and
latitude. ([Here's](https://twitter.com/drob/status/719927537330040832)
a tip if you tend to mix them up.) You can specify popup
text for when you click on the marker with the `popup` 
argument.
```{r}
martiniToren <- c(53.21955619718622, 6.5680924402408785)
my_map <- my_map %>%
  addMarkers(lat = martiniToren[1], lng = martiniToren[2],
             popup = "Martini toren, Groningen")
my_map
```

## Add multiple markers
Adding one marker at a time is often not practical if you
want to display many markers. If you have a data frame with
columns `lat` and `lng` you can pipe that data frame into
`leaflet()` to add all the points at once.
```{r}
df <- data.frame(lat = runif(20, min=martiniToren[1] - 0.1, max=martiniToren[1] + 0.1),
                 lng = runif(20, min=martiniToren[2] - 0.1, max=martiniToren[2] + 0.1))
df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup = paste(martiniToren[1], martiniToren[2]))
```

## Making Custom Markers

The blue markers that leaflet comes packaged with may not be
enough depending on what you're mapping. Thankfully you can
make your own markers from `.png` files.

```{r}
triventoIcon <- makeIcon(
  iconUrl = "https://www.trivento.nl/hubfs/Website-2020/img/trivlogo.png",
  iconWidth = 50, iconHeight = 50 * (585/1200),
  #iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

triventoLatLong <- data.frame(
  lat = c(52.1965808530428),
  lng = c(5.398014240571794))

triventoSite <- "<a href='https://www.trivento.nl/'>Trivento</a>"

triventoLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = triventoIcon, popup = triventoSite)

```

## Adding Multiple Popups
When adding multiple markers to a map, you may want to add
popups for each marker. You can specify a string of plain
text for each popup, or you can provide HTML which will be
rendered inside of each popup.

```{r}
rugIcon <- makeIcon(
  iconUrl = "https://www.rug.nl/_definition/shared/images/marker.png",
  #iconWidth = 31*215/230, iconHeight = 31,
  iconAnchorX = 31*215/230/2, iconAnchorY = 16
)

rugLatLong <- data.frame(
  lat = c(53.249896315224845, 53.219094188597275, 53.219339994886695, 53.237403442601135),
  lng = c(6.525655438977048, 6.563148521621385, 6.563000086099349, 6.531661220552787))

rugSites <- c(
  "<a href='https://www.rug.nl/staff/location/5711/'>KVI-CART</a>",
  "<a href='https://www.rug.nl/staff/location/1211'>Universiteits Bibliotheek</a>",
  "<a href='https://www.rug.nl/staff/location/1111'>Academiegebouw</a>",
  "<a href='https://www.rug.nl/staff/location/5211'>Sprotcentrum</a>"
)

rugLatLong %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = rugIcon, popup = rugSites)
```


## Mapping Clusters
Sometimes you might have so many points on a map that it
doesn't make sense to plot every marker. In these situations
leaflet allows you to plot clusters of markers using
`addMarkers(clusterOptions = markerClusterOptions())`. When
you zoom in to each cluster, the clusters will separate until
you can see the individual markers.
```{r}
df <- data.frame(lat = runif(500, min=martiniToren[1] - 0.1, max=martiniToren[1] + 0.1),
                 lng = runif(500, min=martiniToren[2] - 0.1, max=martiniToren[2] + 0.1))

df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```


## Mapping Circle Markers

Instead of adding markers or clusters you can easily add
circle markers using `addCircleMarkers()`.

```{r}
df <- data.frame(lat = runif(20, min=martiniToren[1] - 0.1, max=martiniToren[1] + 0.1),
                 lng = runif(20, min=martiniToren[2] - 0.1, max=martiniToren[2] + 0.1))

df %>% 
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers()
```

## Drawing Circles

You can draw arbitrary shapes on the maps you create,
including circles and squares. The code below draws a map
where the circle on each city is proportional to the
population of that city.

```{r, echo=FALSE}
md_cities <- data.frame(name = c("Groningen", "Haren", "Hoogezand-Sappemeer", "Bedum", "Winsum", "Delfzijl", 
                                 "Zuidhorn", "Leek"),
                        pop = c(233273, 19860, 34232, 10475, 13560, 24678,
                                18917, 19669),
                        lat = c(53.21990107176437, 53.17414197071955, 53.16541182035367, 53.30041735069393, 53.32788974756013, 53.33243444483125, 53.2489688892776, 53.16601267362363),
                        lng = c(6.5678774827168285, 6.603145682715071, 6.788270540386576, 6.60106461340732, 6.515855389566622, 6.923327952033857, 6.40669074038981, 6.386341684566239))
md_cities %>%
    leaflet() %>%
    addTiles() %>%
    addCircles(weight = 1, radius = sqrt(md_cities$pop) * 12)
```


