---
title: "My Fancy Presentation"
author: "Paul Bruynel"
date: "12 July 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new Slide
Some content

***
This slide has no title

## Slide title

### Top level subheading

#### Second level subheading
##### Third level subheading (but not really)


## Some lists

### Bullet list
- bullet a
- bullet b
- bullet c

### Ordered list
1. item a
2. item b
3. item c

## Formatting

Plain text

*Italicized text*

**Bold text**

Inline code:
`for (i %in% 1:10)`

## Some R output
```{r}
head(mtcars)
```

## R output with comment hashes removed
```{r, comment=""}
head(mtcars)
```

## R output, show code
explicitly set echo=TRUE, it's the default, but on the top of this document the knitr options were set with echo=FALSE
```{r, comment="", echo=TRUE}
head(mtcars)
```

## Just show code, do no show output
```{r, comment="", echo=TRUE, eval=FALSE}
head(mtcars)
```

## Plotting
```{r, echo=TRUE, fig.align='center', fig.cap='My awesome figure'}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="Mpg")
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

